\documentclass[line, margin]{res}

\begin{document}
\name{Alex Hoffer}
\address{636 NW 10th St\\ Corvallis, OR 97330\\ (541) 740-6700}

\begin{resume}
\section{OVERVIEW}
Entry level experience in all aspects of the software engineering process, from architectural design to refactoring and testing. Specific interests in human factors on both ends, such as software usability for end users and software maintainability for developers.

\section{EDUCATION}
Bachelor of Science in Computer Science \\
Bachelor of Science in Psychology \\
Oregon State University, Corvallis, OR \\
Expected to graduate Fall 2017 \\
Courses in Software Engineering, Human Computer Interaction, Web Development, Operating Systems, and more. \\
GPA: 3.68

\section{LANGUAGES USED}
\begin{itemize}
\small
\item C/C++
\item Java
\item Python
\item SQL
\item HTML, CSS, PHP
\item Bash Shell Scripting for Linux
\item JavaScript
\item Microsoft Macro Assembler (MASM)
\item R
\item LaTeX
\end{itemize}

\section{EXPERIENCE}
\textit{REU at Oregon State University} \hfill May 2016-present \\
I am a student researcher under Associate Professor Dr. Anita Sarma and Assistant Professor Dr. Rakesh Bobba. My work concerns the security and privacy of home automation devices, as well as how users configure and use them. Until now, I have spent most of my time doing data analysis on a survey of home automation users that I wrote, but am now pivoting into analyzing the data passed between home automation devices. This opportunity has developed my ability to analyze data (using visualization techniques as well as statistical methodology), design user studies, read technical documents, and understand the security and privacy implications inherent in different network protocol stacks and application layers.  \\ [10pt]

\section{REFERENCES}
Available upon request.

\end{resume}
\end{document}
